\LARGE \bf \papertitle

### 2012-09-14 manuscript.tex
Add labeled h2Bird portrait.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
The authors would like to thank Fernando L. Garcia Bermudez for his assistance with the Vicon motion capture system, and the members of the Biomimetic Millisystems Laboratory and the EECS community at the University of California, Berkeley for their advice and support.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtranS}
\bibliography{}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
The authors would like to thank Fernando Garcia Bermudez for his assistance with the Vicon motion capture system, Andrew Pullin for his help with robot photography, and the members of the Biomimetic Millisystems Laboratory and the EECS community at the University of California, Berkeley for their advice and support.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtranS}
\bibliography{}
